Distributional Trees and Forests

### 2017-10-29 pkg/disttree/inst/draft/draft.Rnw
added text and edited plots
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1669 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: aa95e88ffd121635152b7f9876eba6b2ebb1188b

\begin{figure}[h!]
\begin{center}
%\begin{subfigure}{0.5\textwidth}
<<rain_cross_axams_rmse, fig=TRUE, echo=FALSE>>=
boxplot(rain_rmse[,c(2,3,4)], ylab = "RMSE",
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
@
%\end{subfigure}
\caption{\label{boxplot_rmse_cross}RMSE values of the 10x10 cross validation at the station Axams}
\end{center}
\end{figure}
%\hspace{-1cm}
\begin{figure}[h!]
\begin{center}
%\begin{subfigure}{0.5\textwidth}
<<rain_cross_axams_ll, fig=TRUE, echo=FALSE>>=
boxplot(rain_ll[,c(2,3,4)], ylim = c(-2.8,-1.3), ylab = "log-likelihood",
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
#boxplot(rain_ll)
@
%\end{subfigure}
%\caption{\label{boxplots_rain}Results 10x10 cross validation at the station Axams\\
%left: RMSE, right: log-likelihood}
\caption{\label{boxplot_cross_ll}Log-likelihood values of the 10x10 cross validation at the station Axams}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
<<rain_all_rmse, fig=TRUE, echo=FALSE>>=
  matplot(t(rmse[,2:4]), type = "l", lwd = 1, 
          col = gray(0.5, alpha = 0.5), lty = 1, axes = FALSE, 
          xlab = "", ylab = "RMSE", xlim = c(0.5, 3.5))
  boxplot(rmse[,2:4], add = TRUE)
@
\caption{\label{boxplot_rmse_all}RMSE for predictions over all stations}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
<<rain_all_ll, fig=TRUE, echo=FALSE>>=
  matplot(t(ll[,2:4]), type = "l", lwd = 1, col = gray(0.5, alpha = 0.5), 
          lty = 1, axes = FALSE, 
          xlab = "", ylab = "Log-likelihood", xlim = c(0.5, 3.5), ylim = c(-4,-1))
  boxplot(ll[,2:4], add = TRUE)
@
\caption{\label{boxplot_ll_all}Log-likelihood vallues for predictions over all stations (extracted interval $\[-4,1\]$)}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
%\begin{subfigure}{0.5\textwidth}
<<rain_cross_axams_rmse, fig=TRUE, echo=FALSE>>=
boxplot(rain_rmse[,c(2,3,4)], ylab = "RMSE",
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
@
%\end{subfigure}
\caption{\label{boxplot_rmse_cross}RMSE values of the 10x10 cross validation at the station Axams}
\end{center}
\end{figure}
%\hspace{-1cm}
\begin{figure}[h!]
\begin{center}
%\begin{subfigure}{0.5\textwidth}
<<rain_cross_axams_ll, fig=TRUE, echo=FALSE>>=
boxplot(rain_ll[,c(2,3,4)], ylim = c(-2.8,-1.3), ylab = "Log-likelihood",
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
#boxplot(rain_ll)
@
%\end{subfigure}
%\caption{\label{boxplots_rain}Results 10x10 cross validation at the station Axams\\
%left: RMSE, right: log-likelihood}
\caption{\label{boxplot_cross_ll}Log-likelihood values of the 10x10 cross validation at the station Axams (extracted interval [-2.8,-1.3])}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
<<rain_all_rmse, fig=TRUE, echo=FALSE>>=
  matplot(t(rmse[,2:4]), type = "l", lwd = 1, 
          col = gray(0.5, alpha = 0.5), lty = 1, axes = FALSE, 
          xlab = "", ylab = "RMSE", xlim = c(0.5, 3.5))
  boxplot(rmse[,2:4], add = TRUE,
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
@
\caption{\label{boxplot_rmse_all}RMSE for predictions over all stations}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
<<rain_all_ll, fig=TRUE, echo=FALSE>>=
  matplot(t(ll[,2:4]), type = "l", lwd = 1, col = gray(0.5, alpha = 0.5), 
          lty = 1, axes = FALSE, 
          xlab = "", ylab = "Log-likelihood", xlim = c(0.5, 3.5), ylim = c(-4,-1))
  boxplot(ll[,2:4], add = TRUE,
        names = c("Forest", "GAM (prespecified)", "GAM (boosted)")) 
@
\caption{\label{boxplot_ll_all}Log-likelihood vallues for predictions over all stations (extracted interval [-4,-1])}
\end{center}
\end{figure}
